---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ranchr

<!-- badges: start -->
<!-- badges: end -->

`ranchr` provides data and functions to help you breed great monsters in the game [Monster Rancher 2](https://en.wikipedia.org/wiki/Monster_Rancher_2).

## Installation

You can install the development version of `ranchr` like so:

``` r
# install.packages("devtools")
devtools::install_github("duckmayr/ranchr")
```

## Example

Suppose you had a Mono Eyed (Tiger/Suezo) and Mustardy (Zuum/Suezo) and wanted to know what their combination prospects were.
First you'd create `Monster` class objects representing these parent monsters (their current stats are given in the `stats` argument):

```{r define-parents}
library(ranchr)
Parent1 = Monster(
    name  = "Collie",
    main  = "Tiger",
    sub   = "Suezo",
    stats = c(150, 111, 612, 680, 504, 95)
)

Parent2 = Monster(
    name  = "Marigold",
    main  = "Zuum",
    sub   = "Suezo",
    stats = c(286, 220, 461, 505, 400, 181)
)
```

To get a great monster combination, you need the two parents' *adjusted* stats to match with each other, as well as matching with the child monster type's *baseline* stats.
You know how when you're training a monster, some stats go up faster than others?
Well the same monster attributes that cause these differences in stat gains also lead to a behind-the-scenes "adjustment" in how the stat levels are treated during combination.
"Baseline" stats just refers to the average starting out attributes for a monster type straight from a disc.
If you examine a `Monster` object, it will give you all this information:

```{r examine-parent}
Parent1
```

To test out and see how to `Monster`s would combine, you simply add them together!

```{r combination}
Parent1 + Parent2
```

You can see that this should be a great combination, particularly if you can get another Mono Eyed (Tiger/Suezo) out of it, since both parents and the child monster would have their stats ordered: Skill, Intelligence, Speed, Life, Power, Defense (abbreviated Sk, I, Sp, L, P, D respectively in the output above).

## Special Thanks

Special thanks to Kurasu Soratobu, whose "Monster Rancher: Combining FAQ" provided the necessary data and information to make this package possible; I appreciate his willingness to let me publish his data.
Please see the file `inst/COPYRIGHTS` for relevant copyright information.

## Discrepancies

The data for Kurasu's guide were compiled several years ago for the PlayStation version of Monster Rancher 2.
It's *possible* that some things have changed when they ported the game to iOS, Nintendo Switch, and PC.
If you notice anything that seems off, just [open an issue](https://github.com/duckmayr/ranchr/issues) and let me know.
